### 2019-11-27 monograph/chapters/introduction.tex
Fixed introduction.tex main objective

\begin{enumerate}
    \item Analisar a fundamentação teórica de linguagens formais e
    compiladores;
    \item Analisar o estado da arte das ferramentas que fazem formatação de código~=fonte;
    \lang{%
        \item Propose a unique tool that allowing several and distinct
        programming `best practices' being implemented in several programming languages,
        which can be configured and
        set accordingly to their wishes,
        from a single software working well behaved across all programming languages;
    }{%
        \item Projetar uma ferramenta que permita\advisor{
        a}{} várias e
        diferentes linguagens de programação sejam formatadas utilizando o mesmo conjunto de configurações;
    }
    \lang{%
        \item Moreover,
        explain the differences for other softwares and
        the benefits of a unique tool,
        instead of several heavily different ones.
        From this point,
        a sketch is presented on the problem,
        solutions,
        information as for why to want make such software,
        or even why do we want to beautifying things:
    }{%
        \item Avaliar como esta nova ferramenta difere das demais já existentes.
    }
\end{enumerate}

>>>>

\begin{enumerate}
    \item Analisar a fundamentação teórica de linguagens formais e
    compiladores;
    \item Analisar o estado da arte das ferramentas que fazem formatação de código~=fonte;
    \lang{%
        \item Propose a unique tool that allowing several and distinct
        programming `best practices' being implemented in several programming languages,
        which can be configured and
        set accordingly to their wishes,
        from a single software working well behaved across all programming languages;
    }{%
        \item A partir dos pontos fracos e
        fortes do estado da arte de formatadores,
        propor uma nova ferramenta de formatação de código~=fonte.
    }
    \lang{%
        \item Moreover,
        explain the differences for other softwares and
        the benefits of a unique tool,
        instead of several heavily different ones.
        From this point,
        a sketch is presented on the problem,
        solutions,
        information as for why to want make such software,
        or even why do we want to beautifying things:
    }{%
        \item Avaliar como esta nova ferramenta difere das demais já existentes.
    }
\end{enumerate}
